% LaTeX Curriculum Vitae Template
%
% Copyright (C) 2004-2009 Jason Blevins <jrblevin@sdf.lonestar.org>
% http://jblevins.org/projects/cv-template/
%
% You may use use this document as a template to create your own CV
% and you may redistribute the source code freely. No attribution is
% required in any resulting documents. I do ask that you please leave
% this notice and the above URL in the source code if you choose to
% redistribute this file.

\documentclass[letterpaper]{article}

\usepackage{hyperref}
\usepackage{geometry}
\usepackage{xspace}

% Comment the following lines to use the default Computer Modern font
% instead of the Palatino font provided by the mathpazo package.
% Remove the 'osf' bit if you don't like the old style figures.
\usepackage[T1]{fontenc}
\usepackage[sc,osf]{mathpazo}
\usepackage{amsmath}

\def\name{Gil Vegliach}
\def\footerlink{https://clevercoder.net/wp-content/uploads/2023/09/cv.pdf}

% PDF metadata
\hypersetup{
  colorlinks = true,
  urlcolor = black,
  pdfauthor = {\name},
  pdfkeywords = {software development, software engineer, algorithms, machine learning, ml, computer science, mathematics},
  pdftitle = {\name: Curriculum Vitae},
  pdfsubject = {Curriculum Vitae},
  pdfpagemode = UseNone
}

\geometry{
  body={6.5in, 8.5in},
  left=1.0in,
  top=1.25in
}

% Page headers
\pagestyle{myheadings}
\markright{\name}
\thispagestyle{empty}

% Custom section fonts
\usepackage{sectsty}
\sectionfont{\rmfamily\mdseries\Large}
\subsectionfont{\rmfamily\mdseries\itshape\large}

% Don't indent paragraphs.
\setlength\parindent{0em}

% Make lists without bullets
\renewenvironment{itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{1.5em}
  }
}{
  \end{list}
}

\newenvironment{no-indent-itemize}{
  \begin{list}{}{
    \setlength{\leftmargin}{0em}
  }
}{
  \end{list}
}

\def\tilde{$\scriptstyle\sim$}
\def\bullet{$\circ$\xspace}

\begin{document}

{\huge \name}

\bigskip
\begin{minipage}{0.45\linewidth}
  \begin{tabular}{llll}
    Mobile: & On request
       & Blog: & \href{https://clevercoder.net}{\tt https://clevercoder.net} \\
    Email: & \href{mailto:gil.vegliach@gmail.com}{\tt gil.vegliach@gmail.com} 
       & GitHub: &\href{https://github.com/gilvegliach}{\tt https://github.com/gilvegliach}\\
    Languages: & \textsc{en}, \textsc{de}, \textsc{it} 
       & StackOverflow: & \href{https://bit.ly/gil-so}{\tt https://bit.ly/gil-so} \\      
  \end{tabular}
\end{minipage}

\bigskip
\textsc{Keywords}: 
C++, Machine Learning, Python, AI, AWS, EC2, DynamoDB, JSON, REST, Microservices, Scala, Play 2.x,
SBT, Java, Android, Spring, Maven, Gradle, Dagger~2, Guice, Butterknife, Retrofit, Gson, Espresso, JUnit, 
GHE, Git, Jira, Agile, Scrum.

\section*{Employment}
\begin{no-indent-itemize}
  \item \textsc{Google}, Software Engineer, Z\"urich, Oct 2018--present.
  \begin{itemize}
    \item\bullet Quantitative work to improve Search models and algorithms (C++, Python). 
    \item\bullet Set direction for adjacent engineers. Responsible for the full software cycle of multi-quarter projects.
    \item\bullet Organizes sessions to share knowledge in the team. Helps with organization of team events.
    \item\bullet Mentors new engineers. Interviews engineer candidates.
  \end{itemize}
  \item \textsc{Amazon}, Software Engineer, London, July 2017--July 2018.
  \begin{itemize}
    \item\bullet Integrated a dynamic config service and reduced onboarding time from 2h to some minutes.
    \item\bullet Built a service to transfer auth status from web to devices.
    \item\bullet Developed a solution based on CloudFront to reduce latency and time-in-the-network.
    \item\bullet Refactored metrics and alarms to reduce autocut tickets and decrease on-call burden.
    \item\bullet Responsible for the operations of two tier-1 services with world-scale load.
    \item\bullet On-call and hot fix responsibility for such services.
  \end{itemize}
  \item \textsc{Toptal} (3\% admission rate), Software Engineer, contractor, internet, Apr 2016--June 2017.
  \item \textsc{Zalando}, Software Engineer, Berlin, Mar 2015--May 2017.
  \begin{itemize}
    \item\bullet Developed first high-load mobile API micro-service in Scala, 1000+ rps.
    \item\bullet Implemented a crawler to monitor the content and the availability of home and campaign pages.
    \item\bullet Built a caching layer with Clojure and ElasticCache to tell the login status of a customer.
    \item\bullet Maintained the main Zalando shop app written in Java using Spring.
    \item\bullet Set up CI pipeline in Jenkins to increase dev speed.
    \item\bullet Set architectural patterns in the Android app to improve test coverage.
    \item\bullet Decreased Android app startup time by \tilde 65\% and crash rate to <0.5\%.
    \item\bullet Built a Chrome extension to inject OAuth 2.0 tokens into URL ranges to improve dev productivity.
    \item\bullet Interviewed countless developers, juniors to leads, doubling the Android team in less than 6 months.
    \item\bullet Given internal workshops on testability, unit testing, and code quality.
    \item\bullet Mentored new developers, especially in functional languages like Scala.
  \end{itemize}
  \item \textsc{Cortado AG}, Software Engineer, Berlin, Jun 2013--Feb 2015.
  \begin{itemize}
    \item\bullet Led re-design and implementation of Cortado Corporate and Templace apps.
%    \item\bullet Implemented key components such as preview, navigation, file operations, favorites, and others.
    \item\bullet Implemented Personal Printing app.
%   \item\bullet Collaborated with UX and product teams to assess requirements.
  \end{itemize}
  \item \textsc{National ICT Australia}, Researcher intern, Canberra, Aug--Dec 2012. 
%  \begin{itemize}
%    \item\bullet Asked back to continue previous work after excellent performance.
%    \item\bullet Expanded on the previous solution resulting in multiple scientifical publications.
%  \end{itemize}
  \item \textsc{Siemens}, Software Engineer intern, Munich, Feb--Apr 2012.
%  \begin{itemize}
%    \item\bullet Reduced REAgent start-up time (\tilde 40 sec) replacing Drool Fusion with 
%          ad-hoc algorithms.
%    \item\bullet Optimized queries in Optique which resulted in a demo for external customers.
%  \end{itemize}
  \item \textsc{National ICT Australia}, Researcher intern, Canberra, Aug--Nov 2011. 
%  \begin{itemize}
%    \item\bullet Developed a solution for Android security, published at the Nasa Formal Methods \\
%    \phantom{\bullet }Symposium~2012.
%  \end{itemize}
\end{no-indent-itemize}

\section*{Education}
\begin{no-indent-itemize}
  \item M.Sc. EMCL (Computational Logic in Computer Science), Technische Universit\"{a}t Wien, 2010--Apr 2013,
       Austrian average: 1.2 on a scale 1.0--5.0 (Excellent); thesis mark: 1.0; European mark: A, \tilde US: 3.9-4.0 GPA
  \item B.S. Mathematics, University of Trieste, 2006--2010, mark: 110/110 cum laude, \tilde US: 4.0 GPA.
\end{no-indent-itemize}

\section*{Continuous Learning and Certifications}
\begin{no-indent-itemize}
  \item Machine Learning Specialization by Standford Online on Coursera, (\href{https://bit.ly/ml-specialization}{\tt https://bit.ly/ml-specialization}), score~100\%
  \item AWS Certified Solutions Architect---Associate, 5 Jan 2018, score~87\%
  \item Oracle Certified Programmer, Java SE 5/6 (OCPJP, formerly SCJP), 28 Jun 2012, score~95\%
  \item Oracle Certified Associate, Java SE 5/6 (SCJA), 10 Jul 2010, score~86\%
  \item Big Data Analysis with Scala and Spark by EPFL on Coursera 
        (\href{https://bit.ly/scala-big-data}{\tt https://bit.ly/scala-big-data}), score~100\%
  \item Parallel programming in Scala by EPFL on Coursera 
        (\href{https://bit.ly/scala-parallel-programming}{\tt https://bit.ly/scala-parallel-programming}), score~100\%
  \item Functional Program Design in Scala by EPFL on Coursera 
        (\href{https://bit.ly/scala-functional}{\tt https://bit.ly/scala-functional}), score~100\%
  \item Functional Programming Principles in Scala by EPFL on Coursera 
        (\href{https://bit.ly/scala-principles}{\tt https://bit.ly/scala-principles}), score~100\%
  \item Computational Investing by Georgia Tech on Coursera 
        (\href{https://bit.ly/computational-investing}{\tt https://bit.ly/computational-investing}), score~100\%
  \item Accounting \& Financial Statement Analysis by 365 Careers
        (\href{https://bit.ly/accounting-certification}{\tt https://bit.ly/accounting-certification})
\end{no-indent-itemize}

\section*{Scientific Publications}
\begin{no-indent-itemize}
  \item The ins and outs of first-order runtime verification, 2015, with A.~Bauer and J.~K\"{u}star, 
        {\it Formal Methods in System Design~46(3)}
  \item From propositional to first-order monitoring, 2013, with A.~Bauer and J.~K\"{u}star, 
        {\it Proc. 4th International Conference on Runtime Verification~(RV)}
  \item Runtime Verification meets Android Security, 2012, with A.~Bauer and J.~K\"{u}star, 
        {\it NASA Formal Methods Symposium~(NFM 2012)}
  \item Incomplete Databases: Missing Records and Missing Values, 2012, workshop paper with 
        W.~Nutt and S.~Razniewski, {\it Data Quality in Data Integration Systems (DQIS 2012)}
\end{no-indent-itemize}

\bigskip
\begin{center}
  \begin{footnotesize}
    Last updated: \today \\
    \href{\footerlink}{\texttt{\footerlink}}
  \end{footnotesize}
\end{center}

\end{document}
